\NAME: A framework for Efficient Intrusion Detection in the Internet of Things

### 2015-04-15 paper-euspn15.tex
added Elsevier Procedia style + converted paper

% This paper was submitted to WoWMoM15, but was rejected.

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{url}
\hyphenation{}

@@

\title{
\NAME: A framework for \\
Efficient Intrusion Detection\\
in the Internet of Things
}

\author{\IEEEauthorblockN{Christophe Van Ginneken, Jef Maerien,
Christophe Huygens, Wouter Joosen, Danny Hughes}%
\IEEEauthorblockA{iMinds-DistriNet, KU Leuven\\
3001 Leuven, Belgium\\
\{firstname.lastname\}@cs.kuleuven.be}}

\maketitle

@@

@@

\begin{LaTeXdescription}

@@

\end{LaTeXdescription}

@@

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  sibling distance=20mm,node distance=40mm
  ]
  \node (detection)             [align=center] {Detecting\\Intrusions}
    child {node (anomaly)       [align=center] {Anomaly}}
    child {node (signature)     [align=center] {Signature\\Misuse}}
    child {node (specification) [align=center] {Specification}};
  \node (decision)              [align=center,right=of detection] {Decision\\Making}
    child {node (broadcasting)  [align=center] {Broadcast}}
    child {node (interactive)   [align=center] {Interactive}};
\end{tikzpicture}
}
  \caption{Classification of ID Algorithms}
  \label{fig:classification}
\end{figure}

@@

\begin{figure}[ht]
\captionof{lstlisting}{ID Algorithm Pattern\label{alg:id-algo-pattern}}
\begin{algorithmic}[1]
  \Require{devices: global variable for device information}
  \Function{process\_message}{$msg$}
    \ForEach{$byte \in msg$} \label{alg:id-algo-pattern-loop1}
     \State \dots \Comment{analyze byte-sequences}
    \EndFor
    \Let{$devices_x$}{value}  \Comment{optionally update device info}
    \State \Call{send}{$devices_y$, ``info''} \Comment{optionally exchange info} \label{alg:id-algo-pattern-send1}
  \EndFunction
  \State
  \Function{do\_housekeeping}{}
    \ForEach{$device \in devices$} \label{alg:id-algo-pattern-loop2} \label{alg:id-algo-pattern-common-data}
      \If{$device > \dots$} \Comment{validate recorded value}
        \State \dots \Comment{take actions}
        \State \Call{send}{$device$, ``info''} \Comment{communicate} \label{alg:id-algo-pattern-send2}
      \EndIf
    \EndFor
  \EndFunction
  \State
\end{algorithmic}
\end{figure}

@@

\begin{figure}[ht]
\captionof{lstlisting}{Application pattern of multiple ID algorithms\label{alg:id-algo-application}}
\begin{algorithmic}[1]
  \Let{$msg$}{$network$} \Comment{all observed messages}
  \ForEach{$algorithm \in algorithms$}
    \State \Call{algorithm.progress\_message}{msg}
  \EndFor
  \State \dots
  \Comment{at a given interval}
  \ForEach{$algorithm \in algorithms$}
    \State \Call{algorithm.do\_housekeeping}{}
  \EndFor
\end{algorithmic}
\end{figure}

@@

\begin{figure*}[b]
  \centering
  \scalebox{1}{
\begin{tikzpicture}[
  node distance=9mm,
  ,>=stealth,very thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)   [user]                                      {DSL};
  \node (cg)    [representation,right=of dsl,align=center]  {Code\\Generator};
  \node (code)  [generated,right=of cg]                     {code};
  \node (comp)  [representation,right=of code]              {Compiler};
  \node (image) [generated,right=of comp]                   {image};

@@

\end{tikzpicture}
}

\caption{The high level design of \NAME, showing the resources, processes and
artifacts. A grayscale background represents the level of platform dependency,
with darker shades indicating a higher dependency. Both the source code and the
installable image are artifacts.}

\label{fig:design}
\end{figure*}

@@

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=7mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)  [resource]                                 {DSL};
  \node (sm)   [representation,right=of dsl,align=center] {Semantic\\Model};
  \node (cm)   [representation,right=of sm,align=center]  {Syntactic\\Model};
  \node (code) [resource,right=of cm]        {Code};

@@

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=6mm
  ]
  \node (model) [class,fill=black!10!white] {Model}
      child {node (module) [class,fill=black!10!white] {Module} edge from parent [composite]
        child {node (strategy) [class,align=center,xshift=-10.5mm,fill=black!10!white] {Execution\\Strategy} edge from parent [composite]
          child {node(every) [class,xshift=-9mm,fill=black!10!white] {Every} edge from parent [subclass]}
          child {node (when) [class,xshift=9mm,fill=black!10!white] {When} edge from parent [subclass]}
        }
        child {node (function) [class,xshift=10.5mm] {Function} edge from parent [composite]}
      };
  \node (constant)  [class,right=of module]   {Constant};
  \node (scope)     [class,left=of strategy]  {Scope};
  \node (statement) [class,right=of function] {Statement};
  \node (nodes)     [class,left=of module,xshift=-13mm]    {Nodes\\Domain};

@@

  \draw [composite]  (nodes)    -- (scope);
  \draw [dependency] (strategy) -- (function);
\end{tikzpicture}
}

\caption{Partial Semantic Model for \NAME. Shaded classes indicate the
\emph{event/scheduling} construction around functions to allow interpretation
of the intended functionality.}

\label{fig:meta-model}
\end{figure}

@@

% table goes here, because a spanning table is placed on the next page, relative
% to where it's defined.
\begin{table*}[b]
  \centering
  \begin{tabular}{llrrrrrrr}
\toprule
              &            & base  & \multicolumn{2}{c}{watchdog} & \multicolumn{2}{c}{reputation} & \multicolumn{2}{c}{both} \\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total packets sent\\in a window of 90s}}
              & manual     &    20 &    51 & +155\% &    32 &  +60\% &    63 & +215\%\\
              & generated  &    20 &    49 & +145\% &    32 &  +60\% &    55 & +175\%\\
\cmidrule{2-9}
              & difference &     0 &    -2 &   -4\% &     0 &   0\% &    -8 &   -13\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total bytes sent\\in a window of 90s}}
              & manual     &   476 &  1933 & +306\% &   860 &  +81\% &  2317 & +387\%\\
              & generated  &   476 &  1897 & +299\% &   884 &  +86\% &  2161 & +354\%\\
\cmidrule{2-9}
              & difference &     0 &   -36 &   -2\% &    24 &   +3\% &  -156 &   -7\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{event loop\\average duration ($\mu$s)}}
              & manual     &    48 &    94 &  +96\% &    88 &  +83\% &   149 & +210\%\\
              & generated  &    48 &   121 & +152\% &   121 & +152\% &   138 & +188\%\\
\cmidrule{2-9}
              & difference &     0 &    27 &  +29\% &    33 &  +38\% &   -11 &   -7\%\\
\midrule
image
size (bytes)  & manual     & 10466 & 15530 &  +48\% & 13306 &  +27\% & 18334 &  +75\%\\
              & generated  & 10466 & 18352 &  +75\% & 16376 &  +56\% & 20998 & +101\%\\
\cmidrule{2-9}
              & difference &     0 &  2822 &  +18\% &  3070 &  +23\% &  2664 &  +15\%\\
\bottomrule
  \end{tabular}
  \caption{Results and Side-by-Side Comparison.}
  \label{tbl:results}
\end{table*}

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{literature/referenties}

>>>>

% This paper will be submitted to EUSPN15.

\documentclass[3p,times,procedia]{elsarticle}
\flushbottom
\usepackage{ecrc}
\volume{00}
\firstpage{1}
\journalname{Procedia Computer Science}
\runauth{Christophe Van Ginneken, Jef Maerien,
Christophe Huygens, Wouter Joosen, Danny Hughes}
\jid{procs}
\usepackage{amssymb}
\usepackage[figuresright]{rotating}

@@

\begin{frontmatter}

\dochead{6th International Conference on Emerging Ubiquitous Systems and
Pervasive Networks, EUSPN-2015 and the 5th International Conference on Current
and Future Trends of Information and Communication Technologies in Healthcare,
ICTH 2015,}

\title{
\NAME: A framework for Efficient Intrusion Detection in the Internet of Things
}

\author[a]{Christophe Van Ginneken}
\author[a]{Jef Maerien}
\author[a]{Christophe Huygens}
\author[a]{\\Wouter Joosen}
\author[a]{Danny Hughes}

\address[a]{
iMinds-DistriNet, KU Leuven, 3001 Leuven, Belgium\\
\{firstname.lastname\}@cs.kuleuven.be
}

@@

\begin{keyword}

IoT, Domain Specific Languages, Code Generation, Source Code Optimization,
Intrusion Detection

\end{keyword}

\end{frontmatter}

\vspace*{-10pt}

@@

\begin{description}

@@

\end{description}

@@

\begin{figure}[t]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  sibling distance=20mm,node distance=40mm
  ]
  \node (detection)             [align=center] {Detecting\\Intrusions}
    child {node (anomaly)       [align=center] {Anomaly}}
    child {node (signature)     [align=center] {Signature\\Misuse}}
    child {node (specification) [align=center] {Specification}};
  \node (decision)              [align=center,right=of detection] {Decision\\Making}
    child {node (broadcasting)  [align=center] {Broadcast}}
    child {node (interactive)   [align=center] {Interactive}};
\end{tikzpicture}
}
  \caption{Classification of ID Algorithms}
  \label{fig:classification}
\end{figure}

@@

\begin{algorithm}[t]
  \caption{ID Algorithm Pattern}
  \label{alg:id-algo-pattern}
  \begin{algorithmic}
    \Require{devices: global variable for device information}
    \Function{process\_message}{$msg$}
      \ForEach{$byte \in msg$} \label{alg:id-algo-pattern-loop1}
       \State \dots \Comment{analyze byte-sequences}
      \EndFor
      \Let{$devices_x$}{value}  \Comment{optionally update device info}
      \State \Call{send}{$devices_y$, ``info''} \Comment{optionally exchange info} \label{alg:id-algo-pattern-send1}
    \EndFunction
    \State
    \Function{do\_housekeeping}{}
      \ForEach{$device \in devices$} \label{alg:id-algo-pattern-loop2} \label{alg:id-algo-pattern-common-data}
        \If{$device > \dots$} \Comment{validate recorded value}
          \State \dots \Comment{take actions}
          \State \Call{send}{$device$, ``info''} \Comment{communicate} \label{alg:id-algo-pattern-send2}
        \EndIf
      \EndFor
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[t]
  \caption{Application pattern of multiple ID algorithms}
  \label{alg:id-algo-application}
  \begin{algorithmic}
    \Let{$msg$}{$network$} \Comment{all observed messages}
    \ForEach{$algorithm \in algorithms$}
      \State \Call{algorithm.progress\_message}{msg}
    \EndFor
    \State \dots
    \Comment{at a given interval}
    \ForEach{$algorithm \in algorithms$}
      \State \Call{algorithm.do\_housekeeping}{}
    \EndFor
  \end{algorithmic}
\end{algorithm}

@@

\begin{figure}[b]
  \centering
  \scalebox{1}{
\begin{tikzpicture}[
  node distance=9mm,
  ,>=stealth,very thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)   [user]                                      {DSL};
  \node (cg)    [representation,right=of dsl,align=center]  {Code\\Generator};
  \node (code)  [generated,right=of cg]                     {code};
  \node (comp)  [representation,right=of code]              {Compiler};
  \node (image) [generated,right=of comp]                   {image};

@@

\end{tikzpicture}
}
\caption{The high level design of \NAME, showing the resources, processes and
artifacts. A grayscale background represents the level of platform dependency,
with darker shades indicating a higher dependency. Both the source code and the
installable image are artifacts.}

\label{fig:design}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=7mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt}
]
  \node (dsl)  [resource]                                 {DSL};
  \node (sm)   [representation,right=of dsl,align=center] {Semantic\\Model};
  \node (cm)   [representation,right=of sm,align=center]  {Syntactic\\Model};
  \node (code) [resource,right=of cm]        {Code};

@@

\begin{figure}[t]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  edge from parent fork down,
  sibling distance=5mm, level distance=20mm, node distance=6mm
  ]
  \node (model) [class,fill=black!10!white] {Model}
      child {node (module) [class,fill=black!10!white] {Module} edge from parent [composite]
        child {node (strategy) [class,align=center,xshift=-10.5mm,fill=black!10!white] {Execution\\Strategy} edge from parent [composite]
          child {node(every) [class,xshift=-9mm,fill=black!10!white] {Every} edge from parent [subclass]}
          child {node (when) [class,xshift=9mm,fill=black!10!white] {When} edge from parent [subclass]}
        }
        child {node (function) [class,xshift=10.5mm] {Function} edge from parent [composite]}
      };
  \node (constant)  [class,right=of module]   {Constant};
  \node (scope)     [class,left=of strategy]  {Scope};
  \node (statement) [class,right=of function] {Statement};
  \node (nodes)     [class,left=of module,xshift=-13mm]    {Nodes\\Domain};

@@

  \draw [composite]  (nodes)    -- (scope);
  \draw [dependency] (strategy) -- (function);
\end{tikzpicture}
}
\caption{Partial Semantic Model for \NAME. Shaded classes indicate the
\emph{event/scheduling} construction around functions to allow interpretation
of the intended functionality.}
\label{fig:meta-model}
\end{figure}

@@

@@

\begin{table}[b]
  \caption{Results and Side-by-Side Comparison.}
  \label{tbl:results}
\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}llrrrrrrr@{}}
\toprule
              &            & base  & \multicolumn{2}{c}{watchdog} & \multicolumn{2}{c}{reputation} & \multicolumn{2}{c}{both} \\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total packets sent\\in a window of 90s}}
              & manual     &    20 &    51 & +155\% &    32 &  +60\% &    63 & +215\%\\
              & generated  &    20 &    49 & +145\% &    32 &  +60\% &    55 & +175\%\\
\cmidrule{2-9}
              & difference &     0 &    -2 &   -4\% &     0 &   0\% &    -8 &   -13\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{total bytes sent\\in a window of 90s}}
              & manual     &   476 &  1933 & +306\% &   860 &  +81\% &  2317 & +387\%\\
              & generated  &   476 &  1897 & +299\% &   884 &  +86\% &  2161 & +354\%\\
\cmidrule{2-9}
              & difference &     0 &   -36 &   -2\% &    24 &   +3\% &  -156 &   -7\%\\
\midrule
\multirow{2}{*}{\pbox{\textwidth}{event loop\\average duration ($\mu$s)}}
              & manual     &    48 &    94 &  +96\% &    88 &  +83\% &   149 & +210\%\\
              & generated  &    48 &   121 & +152\% &   121 & +152\% &   138 & +188\%\\
\cmidrule{2-9}
              & difference &     0 &    27 &  +29\% &    33 &  +38\% &   -11 &   -7\%\\
\midrule
image
size (bytes)  & manual     & 10466 & 15530 &  +48\% & 13306 &  +27\% & 18334 &  +75\%\\
              & generated  & 10466 & 18352 &  +75\% & 16376 &  +56\% & 20998 & +101\%\\
\cmidrule{2-9}
              & difference &     0 &  2822 &  +18\% &  3070 &  +23\% &  2664 &  +15\%\\
\bottomrule
  \end{tabular*}
\end{table}

@@

\bibliographystyle{elsarticle-num}
\bibliography{literature/referenties}
